---
title: "STAT 331 Portfolio"
author: "Ashkan Taghavi"
format: 
  html: 
    self-contained: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an A.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from a Lab or Challenge assignment where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2).

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv`

```{r wd-1-csv}
# Lab 4, Import Data Set section
avocado <- read_csv(here("Week 4", "Lab 4", "avocado.csv"))

```

-   `xlsx`

```{r wd-1-xlsx}
# Practice Activity 4, Question 1
military <- read_xlsx(here::here("data", 
                                 "gov_spending_per_capita.xlsx"), 
                      sheet = "Share of Govt. spending", 
                      skip = 7, 
                      n_max = 191)

```

-   `txt`

```{r wd-1-txt}
# Practice Activity 5.2, Setup Section
message <- read_csv(here::here("data" , "scrambled_message.txt")
                      )

```

**WD-2: I can select necessary columns from a dataset.**

```{r wd-2}
# Lab 4, Question 5
top_regions <- avocado_metro_cities %>%
  group_by(region) %>%
  summarize(average = mean(`Total Volume`)) %>%
  slice_max(average, n = 5) %>%
  select(region)
```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   numeric

```{r wd-3-numeric}
# Lab 4, Question 3
avocado_major_region |> 
  filter(
    type == 'organic',
    year == 2017
  ) |>
  group_by(region) |>
  summarize(total = sum(`4046`)) |>
slice_max(total)


```

-   character -- specifically a string

```{r wd-3-string}
# Practice Activity 5.2, Question 3
letter_m <- message %>% 
  filter(str_detect(Word, pattern = "^m"))
print(letter_m)

```

-   factor

```{r wd-3-factor}
# Lab 3, Question 12
hiphop_clean |>
  filter(sex == 'Female' &
       ethnic1 == 'non-white') |>
  group_by(word) |>
  summarize(fammean = mean(familiarity)) |>
  slice_min(fammean)

```

-   date

```{r wd-3-date}
# Practice Activity 5.1, Question 3
thanksgiving <- ymd("2018 11 22")
thanksgiving <- force_tz(thanksgiving, tzone = "America/Los_Angeles")

thanksgiving_int <- (thanksgiving - days(35)) %--% (thanksgiving + days(35))

suspects <- suspects %>%
  filter(Time.Spotted %within% thanksgiving_int)



```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   numeric

```{r wd-4-numeric}
# Lab 4, Question 7
avocado_california |>
  rename("Extra Large" = `4770`,
         "Large" =  `4225`,
         "Small" =  `4046`) |>
  mutate(total = `Extra Large` + Large + Small,
         Extra_Large_Prop =  `Extra Large` / total,
         Large_Prop = Large / total,
         Small_Prop = Small / total) |>
  group_by(region,type) |>
  summarize(Small_Prop = mean(Small_Prop),
            Large_Prop = mean(Large_Prop),
            Extra_Large_Prop = mean(Extra_Large_Prop)) |>
  pivot_longer(Small_Prop:Extra_Large_Prop,
               names_to = "Avocado Size",
               values_to = "Proportion of Mean Avocados Sold") |>
  ggplot() + 
  geom_col(mapping = aes(x = region,y = `Proportion of Mean Avocados Sold`, fill = `Avocado Size`)) + 
  facet_grid(. ~ type) + 
  xlab("Regions in California") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_fill_manual(values = c("lightgreen", "#4393C3", "lightblue"))

```

-   character -- specifically a string

```{r wd-4-string}
# Practice Activity 5.2, Question 5
punct <- message %>%
  mutate(symbols = str_extract_all(Word, pattern = "[[:punct:]]")) %>%
  unnest(symbols) %>%
  filter(nchar(symbols) > 0)
print(punct)

```

-   factor

```{r wd-4-factor}
# Lab 5, Question 3 Part 3
surveys <- surveys |> 
  mutate(day_group = fct_collapse(day_of_week,
                                  "Weekday" = c("Mon", "Tue", "Wed", "Thu", "Fri"),
                                  "Weekend" = c("Sat", "Sun")))

ggplot(data = surveys,
       mapping = aes(x = day_group, fill = day_group)) +
  geom_bar() +
  labs(y = "", x = "Day of the Week Type") +
  scale_fill_discrete(guide = "none") +
  ggtitle("Number of Rodents Captured by Weekday vs Weekend")

## Lab 4, Question 7
hiphop_clean <- hiphop_clean |>
  mutate(ethnic1 = if_else(ethnic == 'white', 'white', 'non-white'),
         ethnic1 = as.factor(ethnic1)
  )


```

-   date

```{r wd-4-date}
# Practice Activity 5.1, Question 6
start_time <- ymd_hms("1970-01-01 00:00:00")
start_time <- force_tz(start_time, tz = ("America/Los_Angeles"))

suspects <- suspects |>
  mutate(diff = difftime(start_time, Time.Spotted, units = "mins")
  ) |>
  filter((as.integer(diff) %% 10) == 0)



```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()`

```{r wd-5-left}
# Challenge 4, Challenge
City <- c('Sacramento', 'LosAngeles','SanFrancisco','SanDiego')
Price <- c(330000, 705000, 1402000, 600000)

HousePrice <- data.frame(City, Price)
avocado_california <- avocado |>
  semi_join(california_cities, by = c('region' = 'california_cities'))

avocado_california |>
  select(AveragePrice, `Total Volume`, type, region) |>
  group_by(region, type) |>
  summarize(med_avocado_price = median(AveragePrice)) |>
  left_join(HousePrice, by = c("region" = "City")) |>
  ggplot(mapping = aes(y = med_avocado_price, x = Price,
                       color = type, shape = region)) +
  geom_point() +
  labs(title = "Relationship between House Prices and Avocados",
       x = "Median Housing Price (by California City)", 
       y = "Median Avocado Price ($)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name = "Avocado Type") +
  scale_shape_manual(values = c(15, 16, 17, 4), name = "City")


```

-   `right_join()`

```{r wd-5-right}

```

-   `inner_join()`

```{r wd-5-inner}


```

-   `full_join()`

```{r wd-5-full}

```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()`

```{r wd-6-semi}
# Challenge 4
HousePrice <- data.frame(City, Price)
avocado_california <- avocado |>
  semi_join(california_cities, by = c('region' = 'california_cities'))
```

-   `anti_join()`

```{r wd-6-anti}
# Lab 4, Question 2
avocado |> 
  anti_join(major_region, by = c('region' = 'major_region')) |>
  anti_join(major_state, by = c('region' = 'major_state')) |>
  filter(region != 'TotalUS') |>
  rename("Small" =  `4046`,
         "Large" =  `4225`,
         "Extra Large" = `4770`)

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()`

```{r wd-7-long}
# Challenge 3, Published Comparisons Section
hiphop_clean %>%
  group_by(ethnic1) %>%
  summarise(across(.cols = intl:unclassifiable, .fns = mean, na.rm = TRUE)) %>%
  pivot_longer(cols = -ethnic1) %>%
  pivot_wider(names_from = ethnic1, values_from = value) %>%
  mutate(difference = `non-white` - white)

```

-   `pivot_wider()`

```{r wd-7-wide}
# Challenge 9, Question 3.2
statesnames_a |> 
  filter(Sex == 'F') |>
  pivot_wider(names_from = Sex, values_from = Count) |>
  filter(Name == 'Allison')  |>
  group_by(State) |>
  summarize(sum(F)) |>
    rename(
         "Number of Female-assigned Babies" = "sum(F)") |>
  kable()

```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

I've done this in the following provided assignments:

I have used Quarto and the here package in every lab and challenge assignment. My Challenge 9 is a great example of a professional looking, reproducible analysis.

**R-2: I can write well documented and tidy code.**

-   Example 1

```{r r-2-1}
# Challenge 3, Second Part of Published Comparisons
hiphop_clean %>%
  group_by(ethnic1) %>%
  summarise(across(.cols = intl:unclassifiable, .fns = mean, na.rm = TRUE)) %>%
  pivot_longer(cols = -ethnic1) %>%
  pivot_wider(names_from = ethnic1, values_from = value) %>%
  mutate(difference = `non-white` - white)
```

-   Example 2

```{r r-2-2}
# Challenge 4
HousePrice <- data.frame(City, Price)
avocado_california <- avocado |>
  semi_join(california_cities, by = c('region' = 'california_cities'))

avocado_california |>
  select(AveragePrice, `Total Volume`, type, region) |>
  group_by(region, type) |>
  summarize(med_avocado_price = median(AveragePrice)) |>
  left_join(HousePrice, by = c("region" = "City")) |>
  ggplot(mapping = aes(y = med_avocado_price, x = Price,
                       color = type, shape = region)) +
  geom_point() +
  labs(title = "Relationship between House Prices and Avocados",
       x = "Median Housing Price (by California City)", 
       y = "Median Avocado Price ($)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name = "Avocado Type") +
  scale_shape_manual(values = c(15, 16, 17, 4), name = "City")
```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example 1

```{r r-3-1}
# Challenge 4
HousePrice <- data.frame(City, Price)
avocado_california <- avocado |>
  semi_join(california_cities, by = c('region' = 'california_cities'))

avocado_california |>
  select(AveragePrice, `Total Volume`, type, region) |>
  group_by(region, type) |>
  summarize(med_avocado_price = median(AveragePrice)) |>
  left_join(HousePrice, by = c("region" = "City")) |>
  ggplot(mapping = aes(y = med_avocado_price, x = Price,
                       color = type, shape = region)) +
  geom_point() +
  labs(title = "Relationship between House Prices and Avocados",
       x = "Median Housing Price (by California City)", 
       y = "Median Avocado Price ($)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name = "Avocado Type") +
  scale_shape_manual(values = c(15, 16, 17, 4), name = "City")
```

-   Example 2

```{r r-3-2}
# Lab 3, Question 12
hiphop_clean |>
  filter(sex == 'Female' &
       ethnic1 == 'non-white') |>
  group_by(word) |>
  summarize(fammean = mean(familiarity)) |>
  slice_min(fammean)

```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   numeric variables

```{r dvs-1-num}
# Lab 2, Question 5
ggplot(data = surveys, mapping = aes(x = weight, y = hindfoot_length)) +  
       geom_point(alpha = 0.8) +
       xlab("Weight (grams)") +
       ylab("Hindfoot Length (mm)")

```

-   numeric variables and categorical variables

```{r dvs-2-num-cat}
# Lab 5, Question 1 Part 1 (Revisiting Lab 2)
ggplot(data = surveys, 
       mapping = aes(y = fct_reorder(species, weight), 
                     x = weight)
       ) +
  geom_jitter(alpha = 0.25, 
              color = "tomato", 
              size = 0.8) +
  geom_boxplot(outlier.shape = NA) +    
  labs(x = "Weight (gm)", 
       y = "", 
       title = "Type of Species by Weight")

```

-   categorical variables

```{r dvs-2-cat}
# Lab 5, Question 3 (Captures over the Week) Part 2
surveys <- surveys |>
  mutate(day_of_week = factor(day_of_week,
                              levels = c("Mon", "Tue", "Wed", "Thu", 
                                         "Fri", "Sat", "Sun")))
ggplot(data = surveys, 
       mapping = aes(x = factor(day_of_week, 
                                levels = c("Mon", "Tue", "Wed", 
                                           "Thu", "Fri", "Sat", "Sun")),
                     fill = day_of_week)) +
  geom_bar() +
  labs(y = "", x = "Day of the Week") +
  scale_fill_discrete(guide = "none") +
  ggtitle("Number of Rodents Captured by Day of Week")

```

-   dates

```{r dvs-2-date}
# Lab 5, Question 2 (Time-Series Plot) Part 1
surveys_summary <- surveys |>
  group_by(genus, date)

ggplot(data = surveys_summary,
       mapping = aes(x = date, y = weight, color = genus)) +
  geom_line() +
  labs(x = "Year", y = "Weight (gm)", color = "Genus")
```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   Example 1

```{r dvs-2-1}
# Lab 4, Question 7
avocado_california |>
  rename("Extra Large" = `4770`,
         "Large" =  `4225`,
         "Small" =  `4046`) |>
  mutate(total = `Extra Large` + Large + Small,
         Extra_Large_Prop =  `Extra Large` / total,
         Large_Prop = Large / total,
         Small_Prop = Small / total) |>
  group_by(region,type) |>
  summarize(Small_Prop = mean(Small_Prop),
            Large_Prop = mean(Large_Prop),
            Extra_Large_Prop = mean(Extra_Large_Prop)) |>
  pivot_longer(Small_Prop:Extra_Large_Prop,
               names_to = "Avocado Size",
               values_to = "Proportion of Mean Avocados Sold") |>
  ggplot() + 
  geom_col(mapping = aes(x = region,y = `Proportion of Mean Avocados Sold`, fill = `Avocado Size`)) + 
  facet_grid(. ~ type) + 
  xlab("Regions in California") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_fill_manual(values = c("lightgreen", "#4393C3", "lightblue"))
```

-   Example 2

```{r dvs-2-2}
# Lab 5, Question 3 Part 2
surveys <- surveys |>
  mutate(day_of_week = factor(day_of_week,
                              levels = c("Mon", "Tue", "Wed", "Thu", 
                                         "Fri", "Sat", "Sun")))
ggplot(data = surveys, 
       mapping = aes(x = factor(day_of_week, 
                                levels = c("Mon", "Tue", "Wed", 
                                           "Thu", "Fri", "Sat", "Sun")),
                     fill = day_of_week)) +
  geom_bar() +
  labs(y = "", x = "Day of the Week") +
  scale_fill_discrete(guide = "none") +
  ggtitle("Number of Rodents Captured by Day of Week")


```

**DVS-3: I show creativity in my visualizations**

-   Example 1

```{r dvs-3-1}
# Challenge 4
HousePrice <- data.frame(City, Price)
avocado_california <- avocado |>
  semi_join(california_cities, by = c('region' = 'california_cities'))

avocado_california |>
  select(AveragePrice, `Total Volume`, type, region) |>
  group_by(region, type) |>
  summarize(med_avocado_price = median(AveragePrice)) |>
  left_join(HousePrice, by = c("region" = "City")) |>
  ggplot(mapping = aes(y = med_avocado_price, x = Price,
                       color = type, shape = region)) +
  geom_point() +
  labs(title = "Relationship between House Prices and Avocados",
       x = "Median Housing Price (by California City)", 
       y = "Median Avocado Price ($)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name = "Avocado Type") +
  scale_shape_manual(values = c(15, 16, 17, 4), name = "City")

```

-   Example 2

```{r dvs-3-2}
# Challenge 2 (Challenge Question: Spicy)

colors <- c("red", "green", "blue",  "purple", "darkorange", "magenta", "turquoise", 
                 "darkgreen")

# Create box plot with specified colors
ggplot(data = surveys, aes(x = weight, y = species, color = genus)) +
  geom_boxplot() +
  scale_color_manual(values = colors) +
  labs(title = "Distribution of Weights for Different Species",
       y = "Species", 
       x = "Weight (grams)", 
       color = "Genus of Rodent") + 
  scale_x_log10()

```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example 1

```{r dvs-4-1}
# Lab 4 Question 5
avocado_metro_cities |>
  group_by(region) |>
  summarize(average = mean(`Total Volume`)) |>
  slice_max(average, n = 5)  |>
  select(region) |>
  left_join(avocado, by = 'region') |>
  ggplot( 
       mapping = aes(x = region, y = `Total Volume`,)) + 
  geom_boxplot() +
  labs(title = "Top 5 Metro Regions with the Most Sold Avocados", 
       y = "Total Volume", x = "Metro Region")

```

-   Example 2

```{r dvs-4-2}
# Lab 5, Question 2 Part 2
surveys_summary <- surveys |> 
  group_by(genus, year) |> 
  summarize(mean_weight = mean(weight))

ggplot(data = surveys_summary, mapping = aes(x = year, y = mean_weight, color = genus)) +
  geom_line() +
  labs(x = "Year", y = "Mean Weight (gm)")

```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1

```{r dvs-5-1}
# Challenge 3, Published Comparisons Code Chunk 2
# Revised code to new format of across function
hiphop_clean %>%
  group_by(ethnic1) %>%
  summarise(across(.cols = intl:unclassifiable, .fns = mean, na.rm = TRUE)) %>%
  pivot_longer(cols = -ethnic1) %>%
  pivot_wider(names_from = ethnic1, values_from = value) %>%
  mutate(difference = `non-white` - white)
```

-   Example 2

```{r dvs-5-2}
# Practice Activity 4
military_clean <- military %>% 
  mutate(across(.cols = `1988`:`2019`,
                .fns = ~ na_if(.x , y = ". .")
                ),
         across(.cols = `1988`:`2019`,
                .fns = ~ na_if(.x, y = "xxx")
                )
         )

```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   Example 1

```{r dvs-6-1}
# Challenge 9, "Importing Dataset" Section
statesnames_a <- read.csv(here::here("Week 9", "Lab 9", "StateNames_A.csv"))
statesnames_a <- statesnames_a |>
  rename("Sex" = "Gender"
         )
statesnames_a |>
  datatable(filter = 'bottom', options = list(pageLength = 100)) |>
  formatStyle(c('Name', 'Year', 'Sex', 'State', 'Count'),  
              color = 'darkred', 
              backgroundColor ='salmon', 
              fontWeight = 'bold')

```

-   Example 2

```{r dvs-6-2}
# Challenge 9, Question 3.1
statesnames_a |> 
  pivot_wider(names_from = Sex, values_from = Count) |>
  filter(Name == 'Allison') |>
mutate(
  across(c('F', 'M'), ~replace_na(.x, 0))) |>
  group_by(State) |>
  summarize(across(F:M, sum)) |>
  rename("Number of Male-assigned Babies" = "M",
         "Number of Female-assigned Babies" = "F") |>
  datatable(
  head(statesnames_a),
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    'Table 1: ', htmltools::em('The Number of babies are mostly Female-assigned ') 
  )) |>
  formatStyle('State',  color = 'blue', backgroundColor = 'green', fontWeight = 'bold')
```

**DVS-7: I show creativity in my tables.**

-   Example 1

```{r dvs-7-1}
# Challenge 9, "Importing Dataset" Section
statesnames_a <- read.csv(here::here("Week 9", "Lab 9", "StateNames_A.csv"))
statesnames_a <- statesnames_a |>
  rename("Sex" = "Gender"
         )
statesnames_a |>
  datatable(filter = 'bottom', options = list(pageLength = 100)) |>
  formatStyle(c('Name', 'Year', 'Sex', 'State', 'Count'),  
              color = 'darkred', 
              backgroundColor ='salmon', 
              fontWeight = 'bold')

```

-   Example 2

```{r dvs-7-2}
# Challenge 9, Question 3.2
statesnames_a |> 
  filter(Sex == 'F') |>
  pivot_wider(names_from = Sex, values_from = Count) |>
  filter(Name == 'Allison')  |>
  group_by(State) |>
  summarize(sum(F)) |>
    rename(
         "Number of Female-assigned Babies" = "sum(F)") |>
  kable()

```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call

```{r pe-1-one-call}
# Challenge 3, Published Comparisons Code Chunk 2
# Revised code to new format of across function
hiphop_clean %>%
  group_by(ethnic1) %>%
  summarise(across(.cols = intl:unclassifiable, .fns = mean, na.rm = TRUE)) %>%
  pivot_longer(cols = -ethnic1) %>%
  pivot_wider(names_from = ethnic1, values_from = value) %>%
  mutate(difference = `non-white` - white)

```

-   `across()`

```{r pe-1-across}
# Practice Activity 4
military_clean <- military %>% 
  mutate(across(.cols = `1988`:`2019`,
                .fns = ~ na_if(.x , y = ". .")
                ),
         across(.cols = `1988`:`2019`,
                .fns = ~ na_if(.x, y = "xxx")
                )
         )
```

-   `map()` functions

```{r pe-1-map-1}
# Lab 8, Full Song
xmas2 <- xmas |>
  mutate(
    day.num = as.character(english::english(Day)), 
    Full.Phrase = pmap_chr(.l = list(num_word = day.num, 
                                     item = Gift.Item, 
                                     verb = Verb, 
                                     adjective = Adjective, 
                                     location = Location), 
                           .f = make_phrase)
  )

map_chr(1:12, ~sing_line(xmas2, .x, Full.Phrase)) |>
  str_c(collapse = "\n") |>
  cat()
```

**PE-2: I can write functions to reduce repetition in my code.**

-   Example 1

```{r pe2-1}
# Challenge 4

HousePrice <- data.frame(City, Price)
avocado_california <- avocado |>
  semi_join(california_cities, by = c('region' = 'california_cities'))

avocado_california |>
  select(AveragePrice, `Total Volume`, type, region) |>
  group_by(region, type) |>
  summarize(med_avocado_price = median(AveragePrice)) |>
  left_join(HousePrice, by = c("region" = "City")) |>
  ggplot(mapping = aes(y = med_avocado_price, x = Price,
                       color = type, shape = region)) +
  geom_point() +
  labs(title = "Relationship between House Prices and Avocados",
       x = "Median Housing Price (by California City)", 
       y = "Median Avocado Price ($)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_color_discrete(name = "Avocado Type") +
  scale_shape_manual(values = c(15, 16, 17, 4), name = "City")
```

-   Example 2

```{r pe2-2}
# Lab 4, Question 14

hiphop_clean |>
  filter(sex == 'Male',
       ethnic == 'white',
       age >= 17,
       age <= 23,
       city >= 10000,
       city <= 60000) |>
  slice_max(bieber) |>
  group_by(subj) |>
  summarize() 

```

**PE-3:I can use iteration to reduce repetition in my code.**

-   `across()`

```{r pe-3-across}
# Challenge 3

hiphop_clean %>%
  group_by(ethnic1) %>%
  summarise(across(.cols = intl:unclassifiable, .fns = mean, na.rm = TRUE)) %>%
  pivot_longer(cols = -ethnic1) %>%
  pivot_wider(names_from = ethnic1, values_from = value) %>%
  mutate(difference = `non-white` - white)

```

-   `map()` functions (Provide 2 Examples)

```{r pe-3-map-1}
# Lab 8, Full Song
xmas2 <- xmas |>
  mutate(
    day.num = as.character(english::english(Day)), 
    Full.Phrase = pmap_chr(.l = list(num_word = day.num, 
                                     item = Gift.Item, 
                                     verb = Verb, 
                                     adjective = Adjective, 
                                     location = Location), 
                           .f = make_phrase)
  )

map_chr(1:12, ~sing_line(xmas2, .x, Full.Phrase)) |>
  str_c(collapse = "\n") |>
  cat()
```

```{r pe-3-map-2}
# Challenge 8, Larger Testing
map_chr(1:12, ~ sing_line(xmas2, .x, Full.Phrase)) |>
  str_c(collapse = "\n") |>
  cat()
```

**PE-4: I can use modern tools when carrying out my analysis.**

-   Example 1

```{r pe-4-1}
# Lab 4, Question 14

hiphop_clean |>
  filter(sex == 'Male',
       ethnic == 'white',
       age >= 17,
       age <= 23,
       city >= 10000,
       city <= 60000) |>
  slice_max(bieber) |>
  group_by(subj) |>
  summarize() 


```

-   Example 2

```{r pe-4-2}
# Lab 3, Question 12
hiphop_clean |>
  filter(sex == 'Female' &
       ethnic1 == 'non-white') |>
  group_by(word) |>
  summarize(fammean = mean(familiarity)) |>
  slice_min(fammean)

```

## Data Simulation & Modeling

**DSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1

```{r dsm-1-1}
# Practice Activity 9

set.seed(1957)

music_man <- function(n_tromb, n_cor, n_reed){
  
  trombones <- rnorm(n_tromb, mean = 4.6, sd = 0.8)
  cornets <- runif(n_cor, min = 1.5, max= 3.5 )
  reeds <- rchisq(n_reed, 4)
  total_weight<- sum(trombones,cornets, reeds)
  
  
  return(total_weight)
  
}

my_weights <- map_dbl(.x = 1:1000, 
                      .f = ~ music_man(n_tromb = 76, 
                                       n_cor = 110, 
                                       n_reed = 1035)
                      ) 
sum(my_weights < 4532)
```

**DSM-2: I can fit a linear regression and extract necessary summary measures.**

-   Example 1

```{r dsm-2-1}
# Lab 9, Modelling the number of Allisons
statesnames_a |> 
  filter(Name == 'Allison')  |>
  group_by(Year) |>
  summarize(sum(Count)) |>
  rename(Number = `sum(Count)`) |>
   lm(Number ~ Year, data = _)
```

-   Example 2

```{r dsm-2-2}
# Lab 9, Residuals of Model
statesnames_a |> 
  filter(Name == 'Allison')  |>
  group_by(Year) |>
  summarize(sum(Count)) |>
  rename(Number = `sum(Count)`) |>
   lm(Number ~ Year, data = _) |>
  broom::augment() |> 
  ggplot(mapping = aes(y = .resid, x = .fitted)) +
  geom_point()

```

## Revising My Thinking

<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->

Upon reflection on thiscourse, I feel like my mindset towards how this class operates combined with my overall general expectation for classes in the future has changed immensely. This stems from the fact that I have never taken a class with this type of grading structure. As a result, when I first entered week one, I felt like I somewhat downplayed what would be expected in the class. I was not really getting down some key dates such as when certain assignments like the pre-week and practice work were due, which lead to me having to rush through the posted coursework on Canvas. For me, it was difficult to find the flow of this course the first couple of weeks, which lead to me feeling behind at times. Going into week 3, I started to have a better understanding of the week to week workload and began organizing my time to allow me the appropriate amount of time to go through the coursework videos and readings, which made me much more prepared and confident with the labs and challenge problems. Because of this change, it allowed me transition from a "catching up" mindset, to a more curious and inquisitive mindset, taking the time to fully understand topics and dive into the curiosity it sparked. I also believe that my start to the course taught me to be more reflective on how ways I can improve. I am really starting to enjoy the format of this class because there is no longer any stress or negative feelings when I get assignments back that I don't get 100% on. Now when I see that I get a "G", my mindset instantly goes to an eagerness of figuring out my mistake and finding way to fix it or better my code. Thus far, every assignment in which I did not fully receive an S on, I made sure to understand my mistake(s) and resubmit a new correct solution with a thoughtful reflection.

## Extending My Thinking

<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->

Going further on what was stated above, once I fell into the flow of the course and shifted my organization and mindset, I began to dive in further when working on the labs and challenge problems. I think this shift can be reflected in my Challenge Problem 3 submission, when I learned how to use pivot_longer/pivot_wider before it presented in class. I wanted to take a different approach the problem and after reading about pivoting I attempted to include it in my code. Another example of extending my thinking can be seen in my Lab 4, I included outside citations to help me replicate the plot in question 7. The original plot I made had overlapping x-axis labels, so I used outside sources to find and learn how use scale_x\_discrete() to have x-axis vertically arranged to be offset. I also researched scale_fill_manual(), to customize the colors of the specific proportions in the my bar plot.

## Peer Support & Collaboration

<!-- Include an image of feedback you gave that you are proud of (either in a peer review or in Discord) -->

I have been to every class, and have tried to actively participate in class discussions when possible. I have also put an emphasis on the effort I put into my peer-code-reviews, making sure to take the time to fully review my peers' submissions and offer genuine feedback. This is important to me, because, just as the same way I expect to receive genuine and useful feedback, I want to provide the same treatment to my peers. I also believe my group and I have done a really great job in participating with each other and being helpful in attempting to answer any questions one of us might have. I have seen my group promote a positive team environment by taking time after class to answer questions, exchange contact information to stay in touch, and even finish practice activities outside the classroom. I put an image of an example of some feedback I gave in my peer review for Lab 5 in the supporting artifacts folder.
