# 

---
title: "Challenge 3"
author: "Ashkan Taghavi"
format: 
  html:
    self-contained: true
    code-tools: true
    code-fold: true
    code-summary: "Show code"
    theme: readable
editor: visual
execute: 
  echo: true
  error: false
---

# Challenge 3

## Necessary Code

```{r}
#| execute:
#| output: FALSE
library(tidyverse)
library(here)
hipHopData <- read_csv(here::here("Week 3", "Lab 3", "hiphop.csv"))
hiphop_clean <- hipHopData |> 
  mutate(
    sex = as.factor(sex),
    ethnic = as.factor(ethnic),
    jayz1 = as.factor(jayz1),
    fam1 = as.factor(fam1),
    boondocks1 = as.factor(boondocks1)
  ) |>
  filter(city != 0,
         county != 0,
         countyBlack != 0
         )
hiphop_clean <- hiphop_clean |>
  mutate(ethnic1 = if_else(ethnic == 'white', 'white', 'non-white'),
          ethnic1 = as.factor(ethnic1)
  )
       
```

## Published Comparisons

```{r}
hiphop_clean |>
group_by(sex) |>
summarise(across(intl:unclassifiable, mean, na.rm = TRUE)) |>
  pivot_longer(cols = -sex) |>
         pivot_wider(names_from = sex, values_from = value) |>
  mutate(difference = `Female` - `Male`)
```

It seems that Intl, Vocal, Classical, and Rock were more prevalent in males. Folk, Country, Pop, Alternative, Hiphop, and Unclassifiable were more prevalent in females

```{r}
hiphop_clean |>
group_by(ethnic1) |>
summarise(across(intl:unclassifiable, mean, na.rm = TRUE)) |>
  pivot_longer(cols = -ethnic1) |>
         pivot_wider(names_from = ethnic1, values_from = value) |>
  mutate(difference = `non-white` - white)
  
```

It seems that Intl, Pop, Hiphop, and Unclassifiable was more prevalent in non-whites. Vocal, Classical, Folk, Rock, Country, and Alternative were more prevalent in whites.

## Study Design Critique - Data Ethics

Two concerns that I have of this data set:

1.  Bias in Study Design: By choosing hip-hop as the basis for learning new words, the study could be influenced by existing biases. Hip-hop is commonly associated with negative connotations towards African American English, and the study's design and outcomes may only serve to reinforce these prejudices, further marginalizing African American English-speaking communities.
2.  Inadequate Cultural Awareness: The examination of African American English and recruitment from a hip-hop based event or group in the study may indicate a lack of cultural understanding from the researchers. This could result in insensitive or incorrect depictions of African American English and hip-hop culture, perpetuating damaging stereotypes.

\
